---
title: "Tidy data/week5/607"
author: "jagruti"
date: "9/30/2017"
output:
  html_document: default
  pdf_document: default
---

## Reading data
```{r,echo = TRUE}
library(tidyr)
library(dplyr)
library(ggplot2)
TTData <- read.csv("TTData.csv")
TTData
```

## Re arrangment for column names.
```{r,echo=TRUE}
colnames(TTData) <- c("Airlines","time_check","Los_Angeles","Phoenix","San_Diego","San_Franscisco","Seattle")
TTData
```

## Analysis for "Tidy" Set
```{r,echo = TRUE}
tidyset <- gather(TTData,Destination,arrival_delay,Los_Angeles:Seattle)
tidyset <- data.frame(tidyset)
tidyset
```

## Analysis to compare arrival delays of two airlines 
### We will use "spread" and "mutate" from package tidyverse.

```{r,echo = TRUE}
tidyset1 <- spread(tidyset,time_check,arrival_delay)
tidyset1
```

#### Check for total flight delays
```{r,echo = TRUE}
total_delays <- tidyset1 %>% gather(time_check,Number_flights,delayed,`on time`)
total_delays
```

```{r,echo = TRUE}
ggplot(total_delays,aes(x= Airlines,y = Number_flights,fill = time_check)) +
geom_bar(stat = "identity") + facet_grid(~Destination)+xlab("Cities") +
ylab("Flights")+ labs(fill = "time_check")
```

#### The graph shows that AM WEST has maximum flights with Phoenix city and delays are comparitively low  to San_franscisco where the flights are delayed more .



### Finding the "Delay ratio" will be next step.

```{r,echo = TRUE}
tidyset2 <- mutate(tidyset1,DRatio = (tidyset1$delayed/(tidyset1$`on time` + tidyset1$delayed)))
tidyset2$Airlines <- as.character(tidyset2$Airlines)
tidyset2
```

```{r,echo = TRUE}
ggplot(tidyset2,aes(x = reorder(Destination,DRatio) , y = DRatio,color = Airlines,group = Airlines))+ geom_line(linetype = "dotted") + geom_point(shape = 20,size = 4) + ggtitle("Delay Comparision") + labs(x = "Destinations", y = "Delay Ratio")
```

#### The delay ratio comparision for both air lines show that delays are higher for 'AM WEST' than for 'ALASKA airline'. THe delays are experienced more in cities 'San_franscisco' and 'Seattle'

## Distribution analysis
```{r,echo = TRUE}
analysis <- summarise(group_by(tidyset2,Airlines),mean(DRatio),sd(DRatio),median(DRatio),aggregate_delay = sum(delayed)/sum(delayed + `on time`))
analysis
```

#### Distribution Analysis shows that ALASKA airline has lower mean (delay ratio) while AM WEST has lower proportion of delayed arrivals overall.




