---
title: "Assignment/week9/607"
author: "Jagruti"
date: "10/26/2017"
output: html_document
---

The New York Times web site provides a rich set of APIs, as described here: http://developer.nytimes.com/docs You’ll need to start by signing up for an API key.
Your task is to choose one of the New York Times APIs, construct an interface in R to read in the JSON data, and transform it to an R dataframe.

```{r,echo = TRUE,suppressPackageStartupMessages()}
library(httr)
library(jsonlite)
library(RCurl)
```

### I chose the geographic API.


### 1) Query I : With Country code "US"

```{r,echo = TRUE}
APIkey <- "&api-key=23b48cef8cb5434b8efec48a494a9a62"
#url <- "http://api.nytimes.com/svc/semantic/v2/geocodes/query.json?(query parameters)&api-key=your-API-key" (general form of query)
base_url <-getURL("http://api.nytimes.com/svc/semantic/v2/geocodes/query.json?country_code=US&api-key=23b48cef8cb5434b8efec48a494a9a62")
req <- fromJSON(base_url)
req <- data.frame(req)
head(req)
```

### Query II : With admin_code = NY 

```{r,echo = TRUE}
APIkey <- "23b48cef8cb5434b8efec48a494a9a62"
base_url1 <-getURL("http://api.nytimes.com/svc/semantic/v2/geocodes/query.json?admin_code1=NY&api-key=23b48cef8cb5434b8efec48a494a9a62")
req1 <- fromJSON(base_url1)
req1 <- data.frame(req1)
head(req1)
```

### Query III : With country_code = "US" and Population = 50000.

```{r,echo = TRUE}
APIkey <- "23b48cef8cb5434b8efec48a494a9a62"
base_url2 <-getURL("http://api.nytimes.com/svc/semantic/v2/geocodes/query.json?feature_class=P&country_code=US&population=50000_&api-key=23b48cef8cb5434b8efec48a494a9a62")
req2 <- fromJSON(base_url2)
req2 <- data.frame(req2)
head(req2)
```













