---
title: "Blooming Mushrooms"
author: "jagruti"
date: "9/3/2017"
output:
  html_document: default
  pdf_document: default
---

As part of assignment 1,We will be studing the "Mushroom dataset" 
available at 
https://archive.ics.uci.edu/ml/datasets/Mushroom.

A) Load the data
==============================================================
```{r,echo = TRUE}
URL <- "https://archive.ics.uci.edu/ml/machine-learning-databases/mushroom/agaricus-lepiota.data"
MushroomsData <- read.table(URL, header = FALSE,  sep = ",")
```
'Head' command provides the slight insight of data without crowding your workspace.

```{r,echo = TRUE}
head(MushroomsData)
```
```{r,echo = TRUE}
str(MushroomsData)
```

B) Subsetting the data
================================================================================
```{r,echo = TRUE}
MushroomsData <- data.frame(MushroomsData)
subdata <- subset(MushroomsData,select = c(V1,V2,V3,V4))
head(subdata)
```

C) Renaming columns 
==============================================================================

```{r,echo = TRUE}
names(subdata) <- c("Edible/Poisonous","cap-shape","cap-surface","cap-color")
head(subdata)
```

C.1) 'table' command comes handy whenever we are stuck with total count of each attribute in dataset.

```{r,echo = TRUE}
table(subdata$`Edible/Poisonous`)
table(subdata$`cap-shape`)
table(subdata$`cap-surface`)
table(subdata$`cap-color`)
```

C.2)"gsub" can be used to rename the abbreviations but we wont be using it  with other columns as 'gsub' replaces every abbreviation and can create unncessary duplication of words.
             
```{r,echo = TRUE}
subdata$`Edible/Poisonous` <- gsub("e","edible",subdata$`Edible/Poisonous`)
subdata$`Edible/Poisonous` <- gsub("p","poisonous",subdata$`Edible/Poisonous`)
```
```{r,echo = TRUE}
subdata1 <- data.frame(subdata)
head(subdata1)
```

C.3) Given below is another way to replace abbreviations [neat and clean]
```{r,echo = TRUE}
subdata1$cap.shape = as.character(subdata1$cap.shape)
subdata1$cap.surface = as.character(subdata1$cap.surface)
subdata1$cap.color = as.character(subdata1$cap.color)
subdata1$cap.shape[subdata1$cap.shape == "x"] = "convex";
subdata1$cap.shape[subdata1$cap.shape == "b"] = "bell";
subdata1$cap.shape[subdata1$cap.shape == "c"] = "conical";
subdata1$cap.shape[subdata1$cap.shape == "f"] = "flat";
subdata1$cap.shape[subdata1$cap.shape == "k"] = "knobbed";
subdata1$cap.shape[subdata1$cap.shape == "s"] = "sunken";

subdata1$cap.surface[subdata1$cap.surface == "f"] = "fibrous"
subdata1$cap.surface[subdata1$cap.surface == "g"] = "grooves"
subdata1$cap.surface[subdata1$cap.surface == "y"] = "scaly"
subdata1$cap.surface[subdata1$cap.surface == "s"] = "smooth"

subdata1$cap.color[subdata1$cap.color == "n"] = "brown"
subdata1$cap.color[subdata1$cap.color == "b"] = "buff"
subdata1$cap.color[subdata1$cap.color == "c"] = "cinnamon"
subdata1$cap.color[subdata1$cap.color == "g"] = "gray"
subdata1$cap.color[subdata1$cap.color == "r"] = "green"
subdata1$cap.color[subdata1$cap.color == "p"] = "pink"
subdata1$cap.color[subdata1$cap.color == "u"] = "purple"
subdata1$cap.color[subdata1$cap.color == "e"] = "red"
subdata1$cap.color[subdata1$cap.color == "w"] = "white"
subdata1$cap.color[subdata1$cap.color == "y"] = "yellow"
head(subdata1)
```

Final dataset required as per task given.
