---
title: "Neo4j"
author: "Jagruti"
date: "11/19/2017"
output:
  html_document: default
  pdf_document: default
---

For this assignment, you should take information from a relational database and migrate it to a NoSQL database of your own choosing.

For the NoSQL database, you may use MongoDB (which we introduced in week 7), Neo4j, or another NoSQL database of your choosing.

Your migration process needs to be reproducible.R code is encouraged, but not required.  You should also briefly describe the advantages and disadvantages of storing the data in a relational database vs. your NoSQL database.

For This project,I worked with datasets from week2 which could be found here:
1) https://raw.githubusercontent.com/solaojp/CUNY-MSDA/master/population.csv
2) https://raw.githubusercontent.com/solaojp/CUNY-MSDA/master/tb_cases.csv

I made very simple graphs to get better understanding of 'Neo4j' with basic queries.

First relational dataset which was migrated in Neo4j(NoSQL database).(Basically building nodes to connect through their common relations ).Node labels are "population and cases".

```{r,echo = TRUE}
library(png)
library(grid)
img <- readPNG("x.png")
grid.raster(img)
```

Query for second dataset to migrate in NoSQL database.

```{r,echo = TRUE}
library(png)
library(grid)
img <- readPNG("y.png")
grid.raster(img)
```

To relate two nodes,the query is shown below.

```{r,echo = TRUE}
library(png)
library(grid)
img <- readPNG("w.png")
grid.raster(img)
```

The final graph shows the relation.

```{r,echo = TRUE}
library(png)
library(grid)
img <- readPNG("z.png")
grid.raster(img)
```


#### Describe the advantages and disadvantages of storing the data in a relational database vs. your NoSQL database

#### Advantages:

1) Cypher, Neo4j’s declarative graph query language, is built on the basic concepts and clauses of SQL but has a lot of additional graph-specific functionality to make it simple to work with your rich graph model without being too verbose.

2) In Cypher the syntax stays clean and focused on domain concepts as the structural connections to find or create are expressed visually.

3) Loading CSV file is much more easy with Neo4j as compared to relational database. Broadly speaking,the import of data is easy with much flexibilty.

Some insights are given on Neo4j's website blog:

a) Modeling data with a high number of data relationships.

b) Flexibly expanding the model to add new data or data relationships.

c) Querying data relationships in real-time


#### Disadvantage:

In my persanal opinion,the learning curve for Neo4j is steep as compared to relational database platforms such as SQL server.
























