---
title: "DATA 607 Final Project: Prediction Systems"
author: "Jagruti Salao and Sarah Wigodsky"
date: "`r Sys.Date()`"
output: ioslides_presentation
---
###Introduction
We will be using data from kaggle.com and participating in a current competition to create a better music recommendation system. The goal is to predict the chances of a user listening to a song repetitively after the first observable listening event.  Since people listen to many different types of music, it is hard to predict what song a person will want to listen to repeatedly.  Through kaggle KKBOX, Asia's leading music streaming service, provides a training data set with information about songs and listeners. 
 
```{r,echo = TRUE,suppressMessages = TRUE, warning=FALSE}
library(ggplot2)
library(dplyr)
library(tm)
library(reshape2)
library(tidyr)
library(stringr)
```

```{r ,echo = TRUE}
members <- read.csv("https://raw.githubusercontent.com/swigodsky/Music-Recommender-System/master/members.csv", stringsAsFactors = FALSE)
members <- members[1:2000,]
colnames(members) <- c("user_id", "city", "age", "gender", "registration_method", "registration_time", "expiration_date")
members$age <- gsub(0, NA, members$age) #replace age that is recorded as zero with NA
members
```

```{r,echo = TRUE}
y <- read.csv ("https://raw.githubusercontent.com/swigodsky/Music-Recommender-System/master/sample_submissionb.csv")
y[1:2000,]
```


```{r,echo = TRUE}
song_extra_info <- read.csv("https://raw.githubusercontent.com/swigodsky/Music-Recommender-System/master/song_extra_infob.csv",header=TRUE, stringsAsFactors=FALSE)
song_extra_info <- song_extra_info[1:2000,]
```

```{r,echo = TRUE}
songs <- read.csv("https://raw.githubusercontent.com/swigodsky/Music-Recommender-System/master/songsd.csv", header=FALSE, stringsAsFactors = FALSE)

#, sep=",", header=FALSE, stringsAsFactors=FALSE, fileEncoding="latin1")
names(songs) = as.character(unlist(songs[1,]))
songs <- songs[-1,]
songs<-songs[1:2000,]
colnames(songs) <- c("song_id", "song_length", "genre_id", "artist_name", "composer", "lyricist", "language")
songs
```

```{r,echo = TRUE}
testdata <- read.csv("https://raw.githubusercontent.com/swigodsky/Music-Recommender-System/master/test.csv", stringsAsFactors = FALSE)
testdata <-testdata[1:2000,]
```

```{r,echo = TRUE}
trainingdata <- read.csv("https://raw.githubusercontent.com/swigodsky/Music-Recommender-System/master/trainb.csv", stringsAsFactors = FALSE)
trainingdata <-trainingdata[1:2000,]
colnames(trainingdata) <- c("user_id", "song_id", "system_tab", "layout_seen", "entry_source", "target")
trainingdata
```

# Merged train sets
```{r,echo = TRUE}
merger1 <- merge(trainingdata,songs,"song_id", all=TRUE)  #all=TRUE gives outer join
merger_train <- merge(members,merger1,"user_id", all=TRUE)
#merger_train <- na.omit(merger_train)
summary(merger_train)
head(merger1)
head(merger_train)

```
```{r,echo = TRUE}
#merger_train$registration_init_time <- as.Date(merger_train$registration_init_time,origin = "1970-01-01")
#merger_train$expiration_date <- as.Date(merger_train$expiration_date,origin = "1970-01-01")
head(merger_train)
```

#Merged test sets
```{r,echo = TRUE}
merger3 <- merge.data.frame(testdata,songs,by = "song_id")
merger_test <- merge.data.frame(merger3,members,by = "user_id")
str(merger_test)
```

```{r,echo = TRUE}
str(merger_train)
ggplot(merger_train,aes(x= source_type))+ theme_bw(base_size = 16) +theme(axis.text.x=element_text(angle=90,hjust=1)) + geom_bar()
```

What we can build our initial prediction is that people listen most of the songs from their local-library. Which has high possibility of recurring songs.

Selecting those users who listened to songs from local-library more than once.(Target = 1 and target = 0)

```{r,echo = TRUE}
#merger_train1 <- merger_train[which(merger_train$target == 1),]
#merger_train2 <- merger_train[which(merger_train$target == 0),]

table(merger_train$target)
prop.table(table(merger_train$target))

```
## This shows 70 % songs are repeated more than once within on month.


Okay, that’s a bit more readable. 70% of songs were repeated more than once. This means we can assume that most of songs were repeated. So are you ready to make your first prediction? We can safely assume that evey song in merge_test was also repeated.

```{r,echo = TRUE}
merger_test$target <- rep(1,2125619)
```

### gender - target model

```{r,echo = TRUE}
table(merger_train$msno)
```


















