---
title: "Aviation Industry"
author: "Jagruti"
date: "10/18/2017"
output:
  html_document: default
  pdf_document: default
---
###For Project 3,I choose 'Aviation' industry to scrap data and make predictions.I scraped data with two airlines

### 1) American Airlines
### 2) British Airways
### The two airlines had around 20-25 openings for 'data analyst' position around the states.The openings listed skills required for position and were used to make predictions for my task.

Loading Packages

```{r,echo = TRUE,message=FALSE,warning= FALSE}
library(rvest)
library(XML)
library(RCurl)
library(splitstackshape)
library(tm)
library(xml2)
library(stringr)
library(qdapRegex)
library(plyr)
library(ggplot2)
```

### Loading and cleaning data

```{r,echo = TRUE,message = FALSE,warning = FALSE}
base_url1 <- "https://jobs.aa.com"
html_data <- readLines("https://jobs.aa.com/search/?q=analyst")
html_data <- grep (".jobTitle-link",html_data,value = TRUE)
html_data <- gsub('.*(href=")',"",html_data)
html_data <- gsub('\">*',"",html_data)
html_data <- gsub('*</a>',"",html_data)
html_data <- gsub('\\s*\\w*$',"",html_data)
html_data <- unlist(strsplit(html_data,split = '/',fixed = TRUE))
```


```{r,echo = TRUE}
html_data1 <-paste(html_data[1],html_data[2],html_data[3],html_data[4],sep = '/')
html_data1 <- paste(base_url1,html_data1,'/',sep = '')
html_data2 <- paste(html_data[6],html_data[7],html_data[8],html_data[9],sep = '/')
html_data2 <- paste(base_url1,html_data2,'/',sep = '')
html_data3 <-paste(html_data[11],html_data[12],html_data[13],html_data[14],sep = '/')
html_data3 <- paste(base_url1,html_data3,'/',sep = '')
html_data4 <-paste(html_data[16],html_data[17],html_data[18],html_data[19],sep = '/')
html_data4<- paste(base_url1,html_data4,'/',sep = '')
html_data5 <-paste(html_data[21],html_data[22],html_data[23],html_data[24],sep = '/')
html_data5<- paste(base_url1,html_data5,'/',sep = '')
html_data6 <-paste(html_data[26],html_data[27],html_data[28],html_data[29],sep = '/')
html_data6<- paste(base_url1,html_data6,'/',sep = '')
html_data7 <-paste(html_data[31],html_data[32],html_data[33],html_data[34],sep = '/')
html_data7<- paste(base_url1,html_data7,'/',sep = '')
html_data8 <-paste(html_data[36],html_data[37],html_data[38],html_data[39],sep = '/')
html_data8<- paste(base_url1,html_data8,'/',sep = '')
html_data9 <-paste(html_data[41],html_data[42],html_data[43],html_data[44],sep = '/')
html_data9<- paste(base_url1,html_data9,'/',sep = '')
html_data10 <-paste(html_data[47],html_data[48],html_data[49],html_data[50],sep = '/')
html_data10<- paste(base_url1,html_data10,'/',sep = '')
html_data11 <-paste(html_data[52],html_data[53],html_data[54],html_data[55],sep = '/')
html_data11<- paste(base_url1,html_data11,'/',sep = '')
html_data12 <-paste(html_data[57],html_data[58],html_data[59],html_data[60],sep = '/')
html_data12<- paste(base_url1,html_data12,'/',sep = '')
html_data13 <-paste(html_data[62],html_data[63],html_data[64],html_data[65],sep = '/')
html_data13<- paste(base_url1,html_data13,'/',sep = '')
html_data14 <-paste(html_data[67],html_data[68],html_data[69],html_data[70],sep = '/')
html_data14<- paste(base_url1,html_data14,'/',sep = '')
html_data15<-paste(html_data[72],html_data[73],html_data[74],html_data[75],sep = '/')
html_data15<- paste(base_url1,html_data15,'/',sep = '')
html_data16 <-paste(html_data[77],html_data[78],html_data[79],html_data[80],sep = '/')
html_data16<- paste(base_url1,html_data16,'/',sep = '')
html_data17 <-paste(html_data[83],html_data[84],html_data[85],html_data[86],sep = '/')
html_data17<- paste(base_url1,html_data17,'/',sep = '')
html_data18 <-paste(html_data[88],html_data[89],html_data[90],html_data[91],sep = '/')
html_data18<- paste(base_url1,html_data18,'/',sep = '')
html_data19 <-paste(html_data[94],html_data[95],html_data[96],html_data[97],sep = '/')
html_data19<- paste(base_url1,html_data19,'/',sep = '')
html_data20 <-paste(html_data[99],html_data[100],html_data[101],html_data[102],sep = '/')
html_data20<- paste(base_url1,html_data20,'/',sep = '')
html_data21 <-paste(html_data[104],html_data[105],html_data[106],html_data[107],sep = '/')
html_data21<- paste(base_url1,html_data21,'/',sep = '')
html_data22 <-paste(html_data[109],html_data[110],html_data[111],html_data[112],sep = '/')
html_data22<- paste(base_url1,html_data22,'/',sep = '')
html_data23 <-paste(html_data[114],html_data[115],html_data[116],html_data[117],sep = '/')
html_data23<- paste(base_url1,html_data23,'/',sep = '')
html_data24<-paste(html_data[119],html_data[120],html_data[121],html_data[122],sep = '/')
html_data24<- paste(base_url1,html_data24,'/',sep = '')
html_data25<-paste(html_data[124],html_data[125],html_data[126],html_data[127],sep = '/')
html_data25<- paste(base_url1,html_data25,'/',sep = '')

html_megaset <- rbind(html_data1,html_data2,html_data3,html_data4,html_data5,html_data6,html_data7,html_data8,html_data9,html_data10,html_data11,html_data12,html_data13,html_data14,html_data15,html_data16,html_data17,html_data18,html_data19,html_data20,html_data21,html_data22,html_data23,html_data24,html_data25)
html_megaset
```

### With all links listed above,to read data from those individual web pages,"xml" package is great help.I used 'for' loop for going through every webpage and reading data with keywords "skill","experience", "language","Job Qualifications".

```{r,echo = TRUE,message= FALSE,warning = FALSE}
t1<-as.character()
for(i in 1:length(html_megaset))
{
  webpage<-getURL(html_megaset[i])
  webpage <- readLines(tc <- textConnection(webpage)); close(tc)
  pagetree <- htmlTreeParse(webpage, error=function(...){}, useInternalNodes = TRUE)
  skillwords1 <-unlist(xpathSApply(pagetree,"/html/body/div/descendant::*[contains (text(),'skills')]",xmlValue))
  skillwords2 <-unlist(xpathSApply(pagetree,"/html/body/div/descendant::*[contains (text(),'experience')]",xmlValue))
  skillwords3 <-unlist(xpathSApply(pagetree,"/html/body/div/descendant::*[contains (text(),'language')]",xmlValue))
  skillwords4 <-unlist(xpathSApply(pagetree,"/html/body/div/descendant::*[contains (text(),'Job Quatlifications')]",xmlValue))
 if (length(paste(skillwords1,skillwords2,skillwords3,skillwords4))>0 )
  { t1[i]<-paste(skillwords1,skillwords2,skillwords3,skillwords4)  }
 else 
t1[i]<-"0"
}

write.table(t1,file = "data1.csv")
file1<-read.csv("data1.csv",header = FALSE,stringsAsFactors = FALSE)
```

### 'file1' had 7 columns with raw data, which is required to transform into single data frame.
### "Corpus" comes under package 'tm' for reading and collecting text document.

```{r,echo = TRUE}
file1$V1<-paste(file1$V1,file1$V2,file1$V3,file1$V4,file1$V4,file1$V5,file1$V6,file1$V7,sep = "")
review_text1 <- paste(file1$V1, collapse=" ")
review_source1 <- VectorSource(review_text1)
c1 <- Corpus(review_source1)
c1 <- tm_map(c1, content_transformer(tolower))
c1 <- tm_map(c1, removePunctuation)
c1 <- tm_map(c1, stripWhitespace)
c1 <- tm_map(c1, removeWords, stopwords("english"))
dtm1 <- DocumentTermMatrix(c1)
dtm21 <- as.matrix(dtm1)
frequency1 <- colSums(dtm21)
frequency1 <- sort(frequency1, decreasing=TRUE)
head(frequency1,200)
```

### Forming skill sets based on 'technical' and 'non techical' category.

```{r,echo = TRUE}
skill_data1<-as.data.frame(frequency1)
skill_data1$skill1<-rownames(skill_data1)

non_tech_skill1<-skill_data1[skill_data1$skill1 %in% c("Self","interpersonal","innovation","creative","curiosity","leadership","team","management","strategy","communication","planning","driven","willing","commitment","attention","proficiency","knowledge","teamwork","focus","selfmotivated"),]


tech_skills1 <- skill_data1[skill_data1$skill1 %in% c("technology","python","microsoft","powerpoint","tableau","simulation","javascrpts","sql","agile","objectoriented","sas","java","javascript","statistical","regression","Rstudio"),]

SoftSkill <- non_tech_skill1$skill1
SFrequency <- non_tech_skill1$frequency1
NTSkills<- tech_skills1$skill1
NTFrequency <- tech_skills1$frequency1
merger1 <- as.data.frame(cbind(SoftSkill,SFrequency))
merger1
merger2 <- as.data.frame(cbind(NTSkills,NTFrequency))
merger2
```

# British Airways

#### (Similar analysis was performed with "British Airways")


```{r,echo = TRUE}
base_url <- "http://careers.united.com/"
dataunited <- readLines("http://careers.united.com/ListJobs/ByKeyword/analyst/")
dataunited <- grep ('<a href=',dataunited,value = TRUE)
dataunited <- grep ('<a href=\"/ShowJob/Id',dataunited,value = TRUE)
dataunited <- gsub(" <a href=",'',dataunited)
dataunited <- gsub('*</a>','',dataunited)
dataunited <- str_trim(dataunited,"left")
dataunited <-  unlist(strsplit(dataunited,split = '/',fixed = TRUE))
dataunited1 <- paste(dataunited[2],dataunited[3],dataunited[4],dataunited[5],sep = '/')
dataunited1 <- paste(base_url,dataunited1,'/',sep = '')
dataunited1
dataunited2 <- paste(dataunited[8],dataunited[9],dataunited[10],dataunited[11],sep = '/')
dataunited2 <- paste(base_url,dataunited2,'/',sep = '')
dataunited2
dataunited3 <- paste(dataunited[14],dataunited[15],dataunited[16],dataunited[17],sep = '/')
dataunited3 <- paste(base_url,dataunited3,'/',sep = '')
dataunited3
dataunited4 <- paste(dataunited[20],dataunited[21],dataunited[22],dataunited[23],sep = '/')
dataunited4 <- paste(base_url,dataunited4,'/',sep = '')
dataunited4
dataunited5 <- paste(dataunited[26],dataunited[27],dataunited[28],dataunited[29],sep = '/')
dataunited5 <- paste(base_url,dataunited5,'/',sep = '')
dataunited5
dataunited6 <- paste(dataunited[32],dataunited[33],dataunited[34],dataunited[35],sep = '/')
dataunited6 <- paste(base_url,dataunited6,'/',sep = '')
dataunited6
dataunited7 <- paste(dataunited[38],dataunited[39],dataunited[40],dataunited[41],sep = '/')
dataunited7 <- paste(base_url,dataunited7,'/',sep = '')
dataunited7
dataunited8 <- paste(dataunited[44],dataunited[45],dataunited[46],dataunited[47],sep = '/')
dataunited8 <- paste(base_url,dataunited8,'/',sep = '')
dataunited8
dataunited9 <- paste(dataunited[50],dataunited[51],dataunited[52],dataunited[53],sep = '/')
dataunited9 <- paste(base_url,dataunited9,'/',sep = '')
dataunited9
dataunited10 <- paste(dataunited[56],dataunited[57],dataunited[58],dataunited[59],sep = '/')
dataunited10<- paste(base_url,dataunited10,'/',sep = '')
dataunited10
dataunited11 <- paste(dataunited[62],dataunited[63],dataunited[64],dataunited[65],sep = '/')
dataunited11 <- paste(base_url,dataunited11,'/',sep = '')
dataunited11
dataunited12 <- paste(dataunited[68],dataunited[69],dataunited[70],dataunited[71],sep = '/')
dataunited12<- paste(base_url,dataunited12,'/',sep = '')
dataunited12
dataunited13<- paste(dataunited[74],dataunited[75],dataunited[76],dataunited[77],sep = '/')
dataunited13 <- paste(base_url,dataunited13,'/',sep = '')
dataunited13
dataunited14 <- paste(dataunited[80],dataunited[81],dataunited[82],dataunited[83],sep = '/')
dataunited14<- paste(base_url,dataunited14,'/',sep = '')
dataunited14
dataunited15<- paste(dataunited[86],dataunited[87],dataunited[88],dataunited[89],sep = '/')
dataunited15 <- paste(base_url,dataunited15,'/',sep = '')
dataunited15
dataunited16<- paste(dataunited[92],dataunited[93],dataunited[94],dataunited[95],sep = '/')
dataunited16<- paste(base_url,dataunited16,'/',sep = '')
dataunited16
dataunited17<- paste(dataunited[98],dataunited[99],dataunited[100],dataunited[101],sep = '/')
dataunited17<- paste(base_url,dataunited17,'/',sep = '')
dataunited17
dataunited18<- paste(dataunited[104],dataunited[105],dataunited[106],dataunited[107],sep = '/')
dataunited18<- paste(base_url,dataunited18,'/',sep = '')
dataunited18
dataunited19<- paste(dataunited[110],dataunited[111],dataunited[112],dataunited[113],sep = '/')
dataunited19<- paste(base_url,dataunited19,'/',sep = '')
dataunited19
dataunited20<- paste(dataunited[116],dataunited[117],dataunited[118],dataunited[119],sep = '/')
dataunited20<- paste(base_url,dataunited20,'/',sep = '')
dataunited20
dataunited21 <- paste(dataunited[123],dataunited[124],dataunited[125],dataunited[126],sep = '/')
dataunited21 <- paste(base_url,dataunited21,'/',sep = '')
dataunited21
dataunited22<- paste(dataunited[129],dataunited[130],dataunited[131],dataunited[132],sep = '/')
dataunited22 <- paste(base_url,dataunited22,'/',sep = '')
dataunited22
dataunited23<- paste(dataunited[135],dataunited[136],dataunited[137],dataunited[138],sep = '/')
dataunited23<- paste(base_url,dataunited23,'/',sep = '')
dataunited23
megasetunited <- rbind(dataunited1,dataunited2,dataunited3,dataunited4,dataunited5,dataunited6,dataunited7,dataunited8,dataunited9,dataunited10,dataunited11,dataunited12,dataunited13,dataunited14,dataunited15,dataunited16,dataunited17,dataunited18,dataunited19,dataunited20,dataunited21,dataunited22,dataunited23)

```

```{r,echo = TRUE,message= FALSE,warning= FALSE}
x1<-as.character()

for(i in 1:length(megasetunited))
{
  webpage<-getURL(megasetunited[i])
  webpage <- readLines(tc <- textConnection(webpage)); close(tc)
  pagetree <- htmlTreeParse(webpage, error=function(...){}, useInternalNodes = TRUE)
 t1<-unlist(xpathSApply(pagetree,"/html/body/div/descendant::*[contains (text(),'skills')]",xmlValue))
 t2<-unlist(xpathSApply(pagetree,"/html/body/div/descendant::*[contains (text(),'Preferred')]",xmlValue))
 t3<-unlist(xpathSApply(pagetree,"/html/body/div/descendant::*[contains (text(),'Required')]",xmlValue))
 t4 <- unlist(xpathSApply(pagetree,"/html/body/div/descendant::*[contains (text(),'Job overview')]",xmlValue))
 t5 <- unlist(xpathSApply(pagetree,"/html/body/div/descendant::*[contains (text(),'proficiency')]",xmlValue))
 if (length(paste(t1,t2,t3,t4,t5))>0 )
   { x1[i]<-paste(t1,t2,t3,t4,t5)  }
 else 
 x1[i]<-"0"
 }
write.csv(x1,file = "united.csv")
file2<-read.csv("united.csv",header = FALSE,stringsAsFactors = FALSE)
file2$V1<-paste(file2$V1,file2$V2,sep = "")
review_text2 <- paste(file2$V1, collapse=" ")
review_source2 <- VectorSource(review_text2)
c2 <- Corpus(review_source2)
c2 <- tm_map(c2, content_transformer(tolower))
c2 <- tm_map(c2, removePunctuation)
c2 <- tm_map(c2, stripWhitespace)
c2 <- tm_map(c2, removeWords, stopwords("english"))
dtm2 <- DocumentTermMatrix(c2)
dtm22 <- as.matrix(dtm2)
frequency2 <- colSums(dtm22)
frequency2 <- sort(frequency2, decreasing=TRUE)
head(frequency2,200)
```

```{r,echo = TRUE}
skill_data2<-as.data.frame(frequency2)
skill_data2$skill2<-rownames(skill_data2)

non_tech_skill2<-skill_data2[skill_data2$skill2 %in% c("Self","interpersonal","innovation","creative","curiosity","leadership","team","management","strategy","communication","planning","driven","willing","commitment","attention","proficiency","knowledge","teamwork","focus","selfmotivated"),]

tech_skills2 <- skill_data2[skill_data2$skill2 %in% c("technology","python","microsoft","powerpoint","tableau","simulation","javascrpts","sas","simulation","javascrpts","sql","agile","objectoriented"),]
```

### Meging and ploting data from both airlines together.

```{r,echo = TRUE}
SoftSkill <- non_tech_skill2$skill2
SFrequency <- non_tech_skill2$frequency2
NTSkills<- tech_skills2$skill2
NTFrequency <- tech_skills2$frequency2
merger3 <- as.data.frame(cbind(SoftSkill,SFrequency))
merger3
merger4 <- as.data.frame(cbind(NTSkills,NTFrequency))
merger4
```

```{r,echo = TRUE}
MegaMerger1 <- rbind(merger1,merger3)
MegaMerger1$SFrequency <- as.integer(MegaMerger1$SFrequency)
MegaMerger1 <- ddply(MegaMerger1,.(SoftSkill),summarize,sum=sum(SFrequency))
MegaMerger1 <-arrange(MegaMerger1,desc(MegaMerger1$sum),SoftSkill)
MegaMerger1$SoftSkill <- as.character(MegaMerger1$SoftSkill)
MegaMerger1
```

```{r,echo = TRUE}
MegaMerger1$SoftSkill <- factor(MegaMerger1$SoftSkill,levels = MegaMerger1$SoftSkill[order(MegaMerger1$sum)])
ggplot(MegaMerger1,aes(x = SoftSkill , y = sum)) + theme_bw(base_size = 16) +theme(axis.text.x=element_text(angle=90,hjust=1)) + geom_bar(stat="identity",fill = "brown")
```

```{r,echo = TRUE}
MegaMerger2 <- rbind(merger2,merger4)
MegaMerger2$NTFrequency <- as.integer(MegaMerger2$NTFrequency)
MegaMerger2 <- ddply(MegaMerger2,.(NTSkills),summarize,sum=sum(NTFrequency))
arrange(MegaMerger2,desc(MegaMerger2$sum),NTSkills)
```

```{r,echo = TRUE}
MegaMerger2$NTSkills <- factor(MegaMerger2$NTSkills,levels = MegaMerger2$NTSkills[order(MegaMerger2$sum)])
ggplot(MegaMerger2,aes(x = NTSkills , y = sum)) + theme_bw(base_size = 16) +
  theme(axis.text.x=element_text(angle=90,hjust=1)) + geom_bar(stat="identity",fill = "brown")
```






























