---
title: "Week2"
author: "jagruti"
date: "9/9/2017"
output:
  html_document: default
  pdf_document: default
---

Choose six recent popular movies.  Ask at least five people that you know (friends, family, classmates, imaginary friends) to rate each of these movie that they have seen on a scale of 1 to 5.  Take the results (observations) and store them in a SQL database.  Load the information into an R dataframe.
Your deliverables should include your SQL scripts and your R Markdown code, posted to GitHub.
```{r,echo = TRUE}
library("RSQLServer")
library("DBI")
```

## Connection of data base to MySQL
```{r,echo = FALSE}
con <- dbConnect(RMySQL::MySQL(),dbname='Movies', host='127.0.0.1',port = 3306,user = 'root',password = "*********")
```

## Loading information into R dataframe.
```{r,echo = TRUE}
xyz <- dbSendQuery(con,"SELECT * FROM Movies")
dbFetch(xyz)
```

## Performing queries
```{r,echo = TRUE}
highrating <- dbGetQuery(con,'select * from movies WHERE Movies = "La La Land";')
highrating
```





