---
title: "Yoga"
author: "Jagruti"
date: "10/7/2017"
output:
  html_document: default
---
#### The dataset from the post of Emilie Bolduc 
#### Link to dataset :https://data.world/dotslashmaggie/google-trends-yoga/workspace/file?filename=20160502_YogaByStateMonth.csv

### Untidy data is sorted to answer following questions:
####1) Where in the US has there been the most interest in yoga?
####2) When people were most interested in yoga in the last 10 years?
####3) Interactive map showing the popularity of Yoga by state.

```{r,echo = TRUE}
library(stringr)
library(tidyr)
library(dplyr)
library(ggplot2)
library(ggmap)
library(leaflet)
data <- read.csv("yoga.csv")
data <- data[-1,]
head(data)
#str(data)
```

```{r,echo = TRUE}
colnames(data) <- c("Year","Alabama","Alaska","Arizona","Arkansas","California","Colorado","Connecticut","Delaware","DC","Florida","Georgia","Hawaii","Idaho","Illinois","Indiana","Iowa","Kansus","Kentucky","Louisiana","Maine","Maryland","Masachusetts","Michigan","Minnesota","Mississippi","Missouri","Montana","Nebraska","Nevada","NH","New_Jersey","New_Mexico","New_York","North_Carolina","North_Dakota","Ohio","Oklahoma","Oregon","Pennsylvania","Rhode_Island","South_Carolina","South_Dakota","Tennessse","Texas","Utah","Vermont","Virginia","Washington","West_Virginia","Wisconsin","Wyoming")
data1  <-data %>% 
            separate(Year,into = c("Year","month"),sep = "-")
data1 <- data1[,-2]
```

```{r,echo = TRUE}
data2 <- data1 %>%
      group_by(Year)%>%
         summarise_all(funs(sum))
data2 <- data.frame(data2)
```

```{r,echo = TRUE}
data3 <- setNames(data.frame(t(data2[,-1])),data2[,1])
for(i in 1:51) {
  data3$total[i] <- rowSums(data3[i,1:13],na.rm = TRUE)
}
head(data3)
max(data3$total)
```

### Vermont(7529) had highest practice of yoga in last 10 years.

```{r,echo = TRUE}
data3[52,] = c(colSums(data3[,1:14]))
max(data3[52,-14])
```

### Year 2015 recorded highest number of yoga practisioners.

```{r,echo = TRUE}
data3$Regions <- c("Alabama","Alaska","Arizona","Arkansas","California","Colorado","Connecticut","Delaware","DC","Florida","Georgia","Hawaii","Idaho","Illinois","Indiana","Iowa","Kansus","Kentucky","Louisiana","Maine","Maryland","Masachusetts","Michigan","Minnesota","Mississippi","Missouri","Montana","Nebraska","Nevada","NH","New_Jersey","New_Mexico","New_York","North_Carolina","North_Dakota","Ohio","Oklahoma","Oregon","Pennsylvania","Rhode_Island","South_Carolina","South_Dakota","Tennessse","Texas","Utah","Vermont","Virginia","Washington","West_Virginia","Wisconsin","Wyoming","Total1")
data3$total <- as.numeric(data3$total)
data3$Regions <- as.character(data3$Regions)
```

### Getting latitudes and longitudes of all states in data frame.
```{r,echo = TRUE}
for (i in 1:nrow(data3)) {
latlon = geocode(data3[i,15])
data3$lon[i] = as.numeric(latlon[1])
data3$lat[i] = as.numeric(latlon[2])
}
```

### Popularity of Yoga by states
```{r,echo = TRUE}
data4 <- data.frame(data3$total, data3$lon, data3$lat,data3$Regions)
colnames(data4) = c('total','lon','lat','Region')
```



```{r,echo = TRUE}
m <- leaflet() %>%
  addTiles() %>%
  addMarkers(lng = data4$lon,lat = data4$lat,popup = paste("Total",data4$total) %>% 
                                                     paste("Region",data4$Region))
m
```
#### Clicking on pins will give the total number of yoga followers in the state.



---
title: "CatFish"
author: "Jagruti"
date: "10/9/2017"
output: pdf_document
---



























